---
output:
  github_document:
    html_preview: false
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "60%"
)
```

# meweasmo R-package: MEta-WEb ASsembly MOdels

[![DOI](https://zenodo.org/badge/130283899.svg)](https://zenodo.org/badge/latestdoi/130283899)

This package simulates the assembly of ecological networks from a regional metaweb. It uses a generalized Lotka-Volterra stochastic model. Species can migrate from the meta-web and establish the ecological interactions specified in the metaweb.

License: MIT

## Installation 

Using the 'devtools' package:

```{r, eval=FALSE}

install.packages("devtools")
library(devtools)
install_github('lsaravia/meweasmo')
library(meweasmo)

```

## Get Started

### Simulate a 6 species network without migration

1) Create a metaweb with a Lotka-Volterra interaction matrix structure, I added one last column with intrinsic growth rate. 

```{r}

library(tibble)

parms <- tibble::tribble(
  ~a1,   ~a2,  ~a3,    ~a4,   ~a5,  ~a6,    ~r,
    0,  4e-6, 3e-5,   2e-5,     0,    0,  -0.01,
-1e-5, -1e-4,    0,   1e-4,  6e-5,    0, -0.001,
-1e-4,     0,    0,      0,  6e-5, 5e-5,  -0.01,
-1e-4,  1e-4,    0,  -5e-4, -1e-5,    0,   0.08,
    0, -1e-4,-1e-4,      0, -1e-6,    0,   0.04,
    0,     0,-1e-4,   2e-4,     0,    0,   0.00
)

```

2) Set the initial conditions and simulate the model with no migration during 1000 time steps

```{r}

library(meweasmo)

yini  <- c(N1 = 100, N2 = 100, N3 = 100, N4 = 100, N5 = 100, N6 = 100)
A <- as.matrix(parms[,1:6])
r<- as.numeric(parms$r)
m <- c(0,0,0,0,0,0)
A1 <- metaWebNetAssemblyGLV(A,m,r,yini,1000,0.1)

```

3) Plot the simulation

```{r}

df1 <- as.data.frame(t(A1$STime))
df1$time <- 1:1000
names(df1) <- gsub("V", "sp", names(df1))
 
library(tidyr)
df1 <- gather(df1,key="Species",value="N", sp1:sp6)

library(ggplot2)
ggplot(df1, aes(time,N,colour=Species)) + geom_point(size=0.1) +  theme_bw() + scale_color_viridis_d()

```

## References


1. Ecological Network assembly: how the regional metaweb influences local food webs
Leonardo A. Saravia, Tomás I. Marina, Marleen De Troch, Fernando R. Momo
bioRxiv 340430; doi: https://doi.org/10.1101/340430